Informing forest carbon inventories under the Paris Agreement using the Global Forest Carbon Database (ForC v4.0)

### 2023-05-23 doc/manuscript/ESSDmanuscript.Rmd
change "transferred" or "sent" to "submitted" #51
@teixeirak, FYI, I also edidted the .RMD.
Not sure why but values in C_variables.csv have changed. let me know if that was expected to you. (for biomass_ag)

n_records_sent_to_EFDB = C_variables[length(C_variables[,"variable"]), "n sent to EFDB"] # n records sent to EFDB
n_relevant_variables_no_records_sent =  sum(C_variables$`n sent to EFDB` == 0,  na.rm = TRUE)
n_relevant_variables_records_sent= n_relevant_variables - n_relevant_variables_no_records_sent
n_records_sent_biomass<- C_variables$`n sent to EFDB`[C_variables$`variable` == "biomass"]
n_records_sent_agb <- C_variables$`n sent to EFDB`[C_variables$`variable` == "biomass_ag"]
n_records_sent_agb_components <- C_variables$`n sent to EFDB`[C_variables$`variable` == "biomass_ag_woody"] + C_variables$`n sent to EFDB`[C_variables$`variable` == "biomass_ag_foliage"]
n_records_sent_rootbiomass <- C_variables$`n sent to EFDB`[C_variables$`variable` == "biomass_root"] 
n_records_sent_rootbiomass_components <- C_variables$`n sent to EFDB`[C_variables$`variable` == "biomass_root_fine"]+C_variables$`n sent to EFDB`[C_variables$`variable` == "biomass_root_coarse"]
n_records_sent_deadwood<- C_variables$`n sent to EFDB`[C_variables$`variable` == "deadwood"] 
n_records_sent_deadwood_components<- C_variables$`n sent to EFDB`[C_variables$`variable` == "deadwood_down"]+C_variables$`n sent to EFDB`[C_variables$`variable` == "deadwood_standing"]
n_records_sent_litter<- C_variables$`n sent to EFDB`[C_variables$`variable` == "litter"] +C_variables$`n sent to EFDB`[C_variables$`variable` == "O.horizon"]
n_records_sent_soil<- C_variables$`n sent to EFDB`[C_variables$`variable` == "SOM / SOC"] 
n_records_sent_stocks = n_records_sent_biomass+n_records_sent_agb+n_records_sent_agb_components+n_records_sent_rootbiomass+n_records_sent_rootbiomass_components+n_records_sent_deadwood+n_records_sent_deadwood_components+ n_records_sent_litter+ n_records_sent_soil
n_records_sent_delta.agb<- C_variables$`n sent to EFDB`[C_variables$`variable` == "delta.agb"]
n_records_sent_delta.litter<- C_variables$`n sent to EFDB`[C_variables$`variable` == "delta.O.horizon"]+C_variables$`n sent to EFDB`[C_variables$`variable` == "delta.litter"]
n_records_sent_increments <- n_records_sent_delta.agb+n_records_sent_delta.litter
n_records_sent_fluxes <- sum(C_variables$`n sent to EFDB`[C_variables$`variable` %in% flux_variables_with_records])
n_records_sent_fluxes_check = n_records_sent_to_EFDB-n_records_sent_stocks-n_records_sent_increments

>>>>

n_records_sent_to_EFDB = C_variables[length(C_variables[,"variable"]), "n submitted to EFDB"] # n records sent to EFDB
n_relevant_variables_no_records_sent =  sum(C_variables$`n submitted to EFDB` == 0,  na.rm = TRUE)
n_relevant_variables_records_sent= n_relevant_variables - n_relevant_variables_no_records_sent
n_records_sent_biomass<- C_variables$`n submitted to EFDB`[C_variables$`variable` == "biomass"]
n_records_sent_agb <- C_variables$`n submitted to EFDB`[C_variables$`variable` == "biomass_ag"]
n_records_sent_agb_components <- C_variables$`n submitted to EFDB`[C_variables$`variable` == "biomass_ag_woody"] + C_variables$`n submitted to EFDB`[C_variables$`variable` == "biomass_ag_foliage"]
n_records_sent_rootbiomass <- C_variables$`n submitted to EFDB`[C_variables$`variable` == "biomass_root"] 
n_records_sent_rootbiomass_components <- C_variables$`n submitted to EFDB`[C_variables$`variable` == "biomass_root_fine"]+C_variables$`n submitted to EFDB`[C_variables$`variable` == "biomass_root_coarse"]
n_records_sent_deadwood<- C_variables$`n submitted to EFDB`[C_variables$`variable` == "deadwood"] 
n_records_sent_deadwood_components<- C_variables$`n submitted to EFDB`[C_variables$`variable` == "deadwood_down"]+C_variables$`n submitted to EFDB`[C_variables$`variable` == "deadwood_standing"]
n_records_sent_litter<- C_variables$`n submitted to EFDB`[C_variables$`variable` == "litter"] +C_variables$`n submitted to EFDB`[C_variables$`variable` == "O.horizon"]
n_records_sent_soil<- C_variables$`n submitted to EFDB`[C_variables$`variable` == "SOM / SOC"] 
n_records_sent_stocks = n_records_sent_biomass+n_records_sent_agb+n_records_sent_agb_components+n_records_sent_rootbiomass+n_records_sent_rootbiomass_components+n_records_sent_deadwood+n_records_sent_deadwood_components+ n_records_sent_litter+ n_records_sent_soil
n_records_sent_delta.agb<- C_variables$`n submitted to EFDB`[C_variables$`variable` == "delta.agb"]
n_records_sent_delta.litter<- C_variables$`n submitted to EFDB`[C_variables$`variable` == "delta.O.horizon"]+C_variables$`n submitted to EFDB`[C_variables$`variable` == "delta.litter"]
n_records_sent_increments <- n_records_sent_delta.agb+n_records_sent_delta.litter
n_records_sent_fluxes <- sum(C_variables$`n submitted to EFDB`[C_variables$`variable` %in% flux_variables_with_records])
n_records_sent_fluxes_check = n_records_sent_to_EFDB-n_records_sent_stocks-n_records_sent_increments
